---
title: "Analytical Method Validation Report"
output:
  pdf_document: default
  html_document: default
  word_document: default
always_allow_html: true
params:
  dataset: NULL
  outliers_estd: NULL
  outliers_std: NULL
  coefficients_overlap: NULL
  coefficients_overlap_plot: NULL
  regression_plot: NULL
  residual_plot: NULL
  regression: NULL
  coef.determination: NULL
  levene: NULL
  durbin_watson: NULL 
  shapiro_wilk: NULL
  anova: NULL
  limits_result: NULL
---

### Dataset Summary
```{r echo=F}
params$dataset %>%
  knitr::kable(caption = "") 

```
## Selectivity
### Results to Matrix Effect
 Bonferroni Outliers Test to External Standard
```{r echo=F}
params$outliers_estd %>%
  knitr::kable(caption = "") 
```

 Bonferroni Outliers Test to Standard Additions
```{r echo=F}
params$outliers_std %>%
  knitr::kable(caption = "") 
```

 Plot overlap 
 
 The linear regression performed to different methods plotted together
```{r echo=F, message=FALSE, warning=FALSE, fig.height=3.5, fig.width=4, dpi=300, fig.align='center'}
print(params$coefficients_overlap_plot)
```

Coefficient Overlap
```{r echo=F}
params$coefficients_overlap%>%
  knitr::kable(caption = "") 
```

## Regression analysis and Linearity
### Regression Plot and Residuals
 Linear Regression and Residuals Graph
 
The regression line in blue, confidence band in gray and prediction band in dashed black line
```{r, echo=F, message=FALSE, warning=FALSE, fig.height=3, fig.width=4, dpi=300, fig.align='center'}
print(params$regression_plot)
```

```{r echo=F, fig.height=3, fig.width=4, dpi=300, message=FALSE, warning=FALSE, fig.align='center'}

print(params$residual_plot)
```

Coefficient of determination
```{r echo=F}
params$coef.determination%>%
  knitr::kable(caption = "") 
```

 Regression terms
```{r echo=F}
params$regression %>%
  knitr::kable(caption = "")
```

Levene homogeineity test
```{r echo=F}
params$levene %>%
  knitr::kable(caption = "") 
```

 Durbin-Watson test to auto-cooreleted errors
```{r echo=F}
params$durbin_watson %>%
  knitr::kable(caption = "") 
```

 Shapiro-Wilk normality test
```{r echo=F}
params$shapiro_wilk %>%
  knitr::kable(caption = "") 
```

 ANOVA of regression and lack-of-fit
```{r echo=F}
params$anova %>%
  knitr::kable(caption = "") 
```

## Limits of detection and quantification
#### LOD and LOQ with calibration curve method
The formula used is LOD = 3.3s/b, and LOQ = 10s/b, where s is the residual standard deviation of a regression line and b the inclination.
The values are in terms of concentration.
```{r, echo=FALSE}
params$limits_result %>%
  knitr::kable(caption = "") 
```


